\section{User Stories}

\subsection{Role of user stories in the project}

Use cases describe interaction structure at analysis level, but they are not the most practical unit for incremental implementation planning. User stories complement the use-case model by expressing development goals from the actor's point of view in a concise form: \emph{As a <role>, I want <goal>, so that <benefit>}. In PizzaHUST, user stories help translate the designed full scope into smaller, testable pieces of work that can be implemented and verified iteratively.

For that reason, the stories below are organized by business epic rather than listed as a single flat backlog. Each story also retains a link to the related use-case ID so that the report can preserve traceability between requirement analysis, design, implementation, and testing.

\subsection{Story organization by epic}

The PizzaHUST backlog is organized into the following epics:

\begin{itemize}
    \item storefront browsing and product customization;
    \item cart, checkout, and order tracking;
    \item authentication, account, and loyalty;
    \item administrative catalog and promotions;
    \item administrative operations and reporting;
    \item kitchen operations and delivery coordination.
\end{itemize}

This epic structure mirrors the system decomposition used later in the architecture and component sections.

\subsection{Customer-facing stories}

\begingroup
\footnotesize
\setlength{\LTpre}{0.4em}
\setlength{\LTpost}{0.8em}
\begin{longtable}{L{0.10\linewidth} L{0.39\linewidth} L{0.28\linewidth} L{0.12\linewidth}}
\caption{Customer-facing user stories}\label{tab:customer-user-stories}\\
\toprule
\textbf{ID} & \textbf{User story} & \textbf{Acceptance criteria summary} & \textbf{Status} \\
\midrule
\endfirsthead
\caption[]{Customer-facing user stories (continued)}\\
\toprule
\textbf{ID} & \textbf{User story} & \textbf{Acceptance criteria summary} & \textbf{Status} \\
\midrule
\endhead
\bottomrule
\endfoot
\bottomrule
\endlastfoot
US-U1 & As a guest, I want to browse active menu categories and items so that I can discover what the store offers. & Active categories and items are shown; unavailable items are not presented as orderable. & Completed \\
US-U2 & As a guest, I want to view item details so that I can decide whether the product fits my needs before ordering. & Item detail view includes name, price context, and relevant customization information. & Completed \\
US-U3 & As a guest, I want to customize a pizza so that I can choose size, crust, and optional toppings before purchase. & Valid selections produce an authoritative quote; invalid combinations are rejected clearly. & Completed \\
US-U4 & As a guest, I want to view combo promotions so that I can compare bundle offers with regular ordering. & Active combos are visible during valid campaign periods. & Completed \\
US-U15 & As a guest, I want to customize combo contents where customer choice is allowed so that the combo matches my preferences. & Eligible selections are constrained by combo definition; invalid slot choices are rejected. & Completed \\
US-U5 & As a guest, I want to manage a cart so that I can review and revise my intended purchase before checkout. & Cart lines can be added, updated, or removed while keeping totals consistent. & Completed \\
US-U6 & As a guest, I want to place a COD order so that I can complete a purchase without online payment. & Valid checkout data creates an order code; unsupported addresses or invalid cart state block submission. & Completed \\
US-U7 & As a guest, I want to track my order by code so that I can see order progress after checkout. & Valid order codes return current status and timeline information. & Completed \\
US-U8 & As a guest, I want to register an account so that I can access customer-specific features later. & Valid registration data creates an account; invalid or duplicate data is rejected. & Completed \\
US-U9 & As a customer, I want to log in so that I can access profile and account-based features securely. & Correct credentials create a session; invalid credentials are rejected safely. & Completed \\
US-U11 & As a customer, I want to view my order history so that I can review previous purchases. & Only the customer's own orders are visible; historical data is preserved. & Completed \\
US-U12 & As a customer, I want to manage my profile so that my account information remains current for future orders. & Profile updates validate allowed fields and preserve account integrity. & Completed \\
US-U13 & As a customer, I want to view my loyalty information so that I can understand my current rewards balance. & Loyalty summary is visible only to the authenticated customer. & Completed \\
US-U14 & As a customer, I want to redeem loyalty points during checkout so that I can reduce my order cost. & Redemption follows business caps and available balance rules. & Completed \\
US-U16 & As a customer, I want to add order-related notes so that the store or courier can follow special handling instructions. & Dish notes and delivery notes are stored in the correct context and do not corrupt pricing or order creation. & Completed \\
\end{longtable}
\endgroup

\subsection{Staff-facing and integration stories}

\begingroup
\footnotesize
\setlength{\LTpre}{0.4em}
\setlength{\LTpost}{0.8em}
\begin{longtable}{L{0.10\linewidth} L{0.39\linewidth} L{0.28\linewidth} L{0.12\linewidth}}
\caption{Staff-facing and integration user stories}\label{tab:staff-user-stories}\\
\toprule
\textbf{ID} & \textbf{User story} & \textbf{Acceptance criteria summary} & \textbf{Status} \\
\midrule
\endfirsthead
\caption[]{Staff-facing and integration user stories (continued)}\\
\toprule
\textbf{ID} & \textbf{User story} & \textbf{Acceptance criteria summary} & \textbf{Status} \\
\midrule
\endhead
\bottomrule
\endfoot
\bottomrule
\endlastfoot
US-A1 & As an administrator, I want to manage pizza items so that the public menu reflects current offerings. & Item creation and modification preserve valid catalog data. & Completed \\
US-A2 & As an administrator, I want to manage options and side dishes so that customizable products can be maintained centrally. & Option rules remain valid and assignable to products. & Completed \\
US-A3 & As an administrator, I want to manage menu categories so that products remain organized for customers and staff. & Categories can be created and updated without breaking item organization. & Completed \\
US-A4 & As an administrator, I want to manage combo campaigns so that the store can run timed promotions. & Validity windows and combo definitions are validated before publication. & Completed \\
US-A5 & As an administrator, I want to monitor orders and dispatch exceptions so that operational problems can be identified and resolved. & Orders remain filterable and retryable only when business rules allow intervention. & Completed \\
US-A6 & As an administrator, I want to manage customer accounts so that I can inspect and control access when needed. & Customer search and account lock/unlock actions respect authorization and data integrity. & Completed \\
US-A7 & As an administrator, I want to view basic sales and order reports so that I can monitor store performance. & Report outputs provide summary information over selected time ranges. & Completed \\
US-K1 & As kitchen staff, I want to view incoming orders so that I know what must be prepared next. & Incoming work is visible in a form suitable for kitchen operation. & Completed \\
US-K2 & As kitchen staff, I want to update preparation status so that the order lifecycle reflects actual kitchen progress. & Only valid status transitions are accepted. & Completed \\
US-K3 & As kitchen staff, I want to mark orders ready for dispatch so that prepared orders can move to delivery handoff. & Dispatch handoff respects state-transition rules and integration outcomes. & Completed \\
US-K4 & As kitchen staff, I want a pickup-confirmation fallback so that dispatch can continue when provider confirmation is unavailable. & Manual fallback is allowed only in valid order states and preserves workflow consistency. & Completed \\
US-T1 & As the delivery service, I want to receive structured delivery requests so that I can accept dispatch work from PizzaHUST. & Delivery requests contain the required information for provider-side handling. & Completed \\
US-T2 & As the delivery service, I want to send signed status callbacks so that PizzaHUST can synchronize delivery progress safely. & Only valid authenticated callbacks can update delivery-related state. & Completed \\
\end{longtable}
\endgroup

\subsection{Traceability from stories to use cases}

User stories are most useful when they remain traceable to analysis and implementation artifacts. Table~\ref{tab:story-traceability} shows representative links between stories, use cases, system elements, and verification targets.

\begingroup
\footnotesize
\setlength{\LTpre}{0.4em}
\setlength{\LTpost}{0.8em}
\captionof{table}{Traceability examples from user stories to design and implementation}\label{tab:story-traceability}
\begin{tabular}{L{0.11\linewidth} L{0.16\linewidth} L{0.23\linewidth} L{0.18\linewidth} L{0.22\linewidth}}
\toprule
\textbf{Story} & \textbf{Use case} & \textbf{Implementation focus} & \textbf{UI/API anchor} & \textbf{Verification anchor} \\
\midrule
US-U3 & U3 Customize Pizza & Pricing and option validation & item detail UI and quote API & backend pricing/option tests and frontend item-flow tests \\
US-U6 & U6 Place COD Order & Checkout and order creation & checkout flow and order API & order-placement tests and smoke flow \\
US-U7 & U7 Track Order & Tracking projection and visibility rules & tracking UI and track API & tracking tests \\
US-A4 & A4 Manage Combo Campaigns & combo CRUD and validity logic & admin combo pages and combo APIs & admin combo tests \\
US-A5 & A5 Monitor Orders and Delivery Exceptions & order-state exception handling & admin orders view and retry-dispatch API & admin order-dispatch tests \\
US-K3 & K3 Mark Order Ready for Dispatch & preparation-to-dispatch transition & kitchen action UI/API & kitchen-action tests \\
US-T2 & T2 Synchronize Delivery Status & webhook validation and state sync & delivery webhook endpoint & delivery webhook tests \\
\bottomrule
\end{tabular}
\endgroup

All user stories listed above are part of the completed full scope of PizzaHUST, and the table is retained for traceability to use cases, implementation anchors, and tests.
